descriptive_Clusters

### 2021-03-13 src/descriptive_Clusters.Rmd
Updated descriptive clusters, paper section 4, and response to reviewers.

LAD.cluster <- paste(path, "/data/temp/clusters_nodiff.csv", sep = "")

@@

#plot largest 5 clusters first - all over 1 million pop

@@

cluster.up <- cluster.up[which(cluster.up$up.LADs > 9),]

@@

UpClusterL <- ggplot(cluster.up, aes(help.date.time, mean.up, 

@@

#export UpClusterL plot for paper
out.plot <- paste(path, "/paper/v1/figures/UpClusterL.png", sep = "")
png(out.plot)
UpClusterL
dev.off()

@@

#export UpClusterS plot for paper
out.plot <- paste(path, "/paper/v1/figures/UpClusterS.png", sep = "")
png(out.plot)
UpClusterS
dev.off()

>>>>

LAD.cluster <- paste(path, "/data/temp/clusters_nodiff_9.csv", sep = "")

@@

#plot largest 6 clusters - all over 500k pop

@@

cluster.up <- cluster.up[which(cluster.up$up.LADs > 4),]

@@

UpCluster <- ggplot(cluster.up, aes(help.date.time, mean.up, 

@@

#export UpClusterL plot for paper
out.plot <- paste(path, "/paper/v1/figures/UpCluster.png", sep = "")
png(out.plot)
UpClusterL
dev.off()

@@

#export UpClusterS plot for paper
#out.plot <- paste(path, "/paper/v1/figures/UpClusterS.png", sep = "")
#png(out.plot)
#UpClusterS
#dev.off()
